---
title: "Pairwise Estimation"
author: "Ken Bredemeyer"
date: "29 April 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Estimating Ability Locations with the PairwiseComparisons package
## Simple Estimation
load package:
```{r load}
library(PairwiseComparisons)
```

Use the 2018 Graduate Teacher Performace Assessment as an example. 

Create a data matrix with `pairs_format2`.  If no extremes, estimate with `estimate`.

```{r}
gtpa_dm <- pairs_format2(gtpa18)
has_extremes(gtpa_dm)
betas <- estimate(gtpa_dm)
head(betas, 4)
```

## Partitioning 
Partion the GTPA data on judges:
```{r partition}
judge_set1.dm <- pairs_format2(gtpa18, judges = 1:20) 
judge_set2.dm <- pairs_format2(gtpa18, judges = 21:40)

has_extremes(judge_set1.dm)
has_extremes(judge_set2.dm)
```
Judge set 1 has no extremes and judge set 2 has extremes
Estimate judge set 1 as above:
```{r}
judge_set1.betas <- estimate(judge_set1.dm)
```
Estimate judge set 2 by first removing extremes, then anchoring on the betas with extremes removed:
```{r extremes}
judge_set2.dm_small <- remove_xtrms(judge_set2.dm)
# which performances are extreme (extreme performance labels are stored as attributes of ... .dm_small
judge_set2.extremes <- xtrms(judge_set2.dm_small)
# estimate with extremes removed
judge_set2.betas_small <- estimate(judge_set2.dm_small)
# estimate, anchoring on betas with extremes removed
judge_set2.betas <- estimate_anch(judge_set2.dm, judge_set2.extremes, judge_set2.betas_small$b)

head(judge_set2.betas)
```

## Alternatively - 
Use `estimate_betas`:
```{r faster}
js1.betas <- estimate_betas(judge_set1.dm)
js2.betas <- estimate_betas(judge_set2.dm)
```
`estimate_betas` wraps above workflow, using `estimate_anch`.
